---
title: "Grades Report"
author: "Ted Thompson"
date: "December 7, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Do females perform better than males in school?

This analysis attempts to answer.Do females perform better than males in school given all other factors are the same? And what is the most influential factor that decides how well a student performs.The hypothesis presesnted is the average performance of female students differ from the average perfromace of male students.

This project uses the Student Performance Data Set (http://archive.ics.uci.edu/ml/datasets/Student+Performance) from the UCI machine learning repositiry. I to use R to wrangle the data organize and create new features. I also have a summary table summarizing key statistics. A boxplot is shown for my visulization.


```{r}
library(tidyverse)
library(broom)
```

## Load Data

```{r}
dat1 <- read.table('https://raw.githubusercontent.com/TeddTech/student_data/master/student-mat.csv',sep=";",header=TRUE)

dat2 <- dat1 %>% mutate(average_grade = (G1+ G2+ G3)/3)
dat2
```


```{r}
boxplot(dat2$average_grade~dat2$sex,
        las=1, ylab="Grade", xlab="Gender", main="Difference Grades Between Male and Females")
```

```{r}
table(dat2$sex)

```


```{r}
(ttest <- t.test(dat2$average_grade~dat2$sex, paired=F, var.eq=T))
tidy(ttest)
```

Because the alpha value used in this analysis is 0.05 there is a statistically signifacant difference the perfomance of males vs females in school. Since the null hypothesis was rejected 0.046 which is very close to 0.05 further test are recommended. In future studies one can consider the many other variables that are included in the data set used. Another thing that could be considered is conduct the study over differenct subjects.
